Supplementary Information

### 2021-04-08 doc/manuscript/ForestGEO_treerings.Rmd
add table 2 to manuscript .rmd

---
title: ''
output: 
    #pdf_document: 
    bookdown::word_document2: 
      reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
bibliography: references.bib
csl: global-change-biology.csl

@@

\newpage
**Table 1 | (DRAFT hypothesis table-- needs to be filled in and condensed/ cleaned up)**. .... 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
hypotheses_table <- read.csv("tables_figures/hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses_table, select = -c(table_row, category, notes) )#remove columns that shouldn't be included
ft <- flextable(hypotheses_table)
ft <- autofit(ft)
ft <- footnote( ft, i = 1, j = 2,
                value = as_paragraph(
                  c("SSC= species-site combinations; SSCV=species-site-variable combination")
                ),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft

@@

**Table 2 | Sites included in this analysis**. Here and throughout, sites are ordered by descending mean annual temperature. Additional site information is provided in Appendix `r site_details_appendix` and Table `r site_details`, and tree species and sampling details are detailed in Tables `r species_table`-`r sampling_details_table`. 
![ ](tables_figures/sites_table.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @alfaro-sanchez_growth_2017; @helcoski_growing_2019 @gonzalez-akre_scbi-forestgeoscbi-forestgeo-data_2020-1; @bumann_assessing_2019; @samonil_individual-based_2013; @kaspar_speciesspecific_2021; @alexander_potential_2019; @finzi_carbon_2020; @birch_birch_2020; @birch_birch_2020b; @birch_birch_2020c; @birch_birch_2020d
---

>>>>

---
title: ''
output: 
    #pdf_document: 
    bookdown::word_document2: 
      reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
  #officedown::rdocx_document
bibliography: references.bib
csl: global-change-biology.csl

@@

\newpage
**Table 1 | (DRAFT hypothesis table-- needs to be filled in and condensed/ cleaned up)**. .... 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
hypotheses_table <- read.csv("tables_figures/hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses_table, select = -c(table_row, category, notes) )#remove columns that shouldn't be included
ft <- flextable(hypotheses_table)
ft <- autofit(ft)
ft <- footnote( ft, i = 1, j = 2,
                value = as_paragraph(c("SSC= species-site combinations; SSCV=species-site-variable combination")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft

@@

**Table 2 | Sites included in this analysis**. Here and throughout, sites are ordered by descending mean annual temperature. Additional site information is provided in Appendix `r site_details_appendix` and Table `r site_details`, and tree species and sampling details are detailed in Tables `r species_table`-`r sampling_details_table`. 
![ ](tables_figures/sites_table.png)

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8)
sites_table<- read.csv("tables_figures/sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
sites_table <- subset(sites_table, select = -c(MAT, JulyTsd, JanTsd, MAPsd)) #drop MAT column, plus columns with sd
ft <- flextable(sites_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .5)
ft <- width(ft, 2:3, width = 1)
ft <- width(ft, 4:6, width = .45)
ft <- width(ft, 7, width = .66)
ft <- width(ft, 8, width = .52)
ft <- width(ft, 9, width = .5)
ft <- width(ft, 10, width = 1.5)
ft <- footnote( ft, i = 1, j = 4:6,
                value = as_paragraph(c("Refers to 1950-2019 mean climate.")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft

```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @alfaro-sanchez_growth_2017; @helcoski_growing_2019 @gonzalez-akre_scbi-forestgeoscbi-forestgeo-data_2020-1; @bumann_assessing_2019; @samonil_individual-based_2013; @kaspar_speciesspecific_2021; @alexander_potential_2019; @finzi_carbon_2020; @birch_birch_2020; @birch_birch_2020b; @birch_birch_2020c; @birch_birch_2020d
---
